A Switching Planner for Combined Task and Observation Planning

### 2010-11-30 code/subarchitectures/planner.sa/trunk/src/latex/ICAPS-2011/evaluation.tex
changes to the bibliography and evaluation text

To test our approach we use a robot exploration domain based on a
scenario from our physical robotic system. Here, a robot is
exploring an office or living environment, and trying to report the
locations of objects to their owner.

% \begin{figure}[h]
%   \centering
%   \input{figures/dora}
%   \caption{A exploration domain with three rooms and 13 places. The
%     robot is in in the centre of room A}
% \label{fig:dora2}
% \end{figure}
% An instance of this domain is shown in figure \ref{fig:dora2}. 
Basic types of element are {\tt rooms}, {\tt places} and {\tt
  objects}. Places are topological map nodes that occur in rooms.
Objects, including the robot, are always located at a place. The robot
can move around the rooms via connections between places given by the
{\tt connected} predicate. Each room has a, possibly unknown, {\em
  category} (e.g. kitchen, office, living room) and depending on this
category, objects are placed inside the rooms.

The robot can look for an object at a place by executing a {\tt
  look-for-object} action. Moreover, the contents of a room indicate
its category, because certain objects are more likely to be located in
rooms of particular categories. For example, a box of cornflakes is
more likely to be located in the kitchen than the office. Executing
{\tt look-for-object} results in a noisy sensing outcome, sometimes
indicating a positive perception if the object is there. Here, some
objects are harder to detect than others. Lastly, if the robot is in
the presence of a human, it can ask what type of room it is currently
in, however conducting a dialogue is more costly than running a vision
algorithm (cost of 8 vs costs of 3).

>>>>

To test our approach we use a robot exploration domain based on a
scenario from our physical robotic system. Here, a robot is exploring
an office or living environment, and trying to report the locations of
objects to their owner. Basic types are {\tt rooms}, {\tt places} and
{\tt objects}. Places are topological map nodes that occur in rooms.
Objects, and also the robot, are always located at a place. The robot
can move around the rooms via connections between places given by a
{\tt connected} predicate. Each room has a, possibly unknown, {\em
  category} (e.g. kitchen, office, living room). Certain objects are
more likely to be located in rooms of a particular category.  For
example, a box of cornflakes is more likely to be located in the
kitchen than the office. The robot can look for an object at a place
by executing a {\tt look-for-object} action. Executing {\tt
  look-for-object} results in a noisy sensing outcome, sometimes
indicating a positive perception if the object is there. We have that
some objects are harder to detect than others. Finally, if the robot
is in the presence of a human, it can ask what type of room it is
currently in, however conducting a dialogue is more costly than
running a vision algorithm (cost of 8 vs costs of 3).
